Equipo 7

### 2021-05-03 final/script.Rmd
Update script.Rmd

@@

>>>>

# cambio nombres

names(censo_localidad10)[names(censo_localidad10) == "Entidad"] <- "NOM_ENT"
names(censo_localidad10)[names(censo_localidad10) == "Municipio"] <- "NOM_MUN"
names(censo_localidad10)[names(censo_localidad10) == "Localidad"] <- "NOM_LOC"

@@

#Ahora para el 2010
#base de datos del 2010
data2<-as.data.frame(merge(planea_localidad10,censo_localidad10, by= c("NOM_ENT","NOM_MUN","NOM_LOC"))) %>% na.omit()

#convierto variables de interes a numéricas
names<-c("esp_1","esp_II","esp_1II","esp_IV",    
         "mat_1","mat_II","mat_1II","mat_IV",
         "top_50_esp","top_50_mat",
         "VIVTOT", "TVIVPAR","VIVPAR_HAB","VPH_INTER","VPH_PC",
         "internet","lap" )  
for (i in names){
  data2[[i]] <- as.numeric(data2[[i]])
}

a<-lm(top_50_mat10~internet,data2)
b<-lm(top_50_mat10~lap,data2)
c<-lm(top_50_esp10~internet,data2)
d<-lm(top_50_esp10~lap,data2)
